---
title: "Problem Set 4"
author: "Marc Ishak"
output:
  html_notebook:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Uni/2019T3/econ3203")

```



# Question 1
## a

```{r}
library(ggplot2)
library(dplyr)

# set.seed(80085) # for reproducibility 

df <-  data.frame(w = rnorm(1000))

# w <- sapply(x, function(q){pnorm(q)})

df <- df %>% 
  arrange(w) %>% 
  mutate(x = pnorm(w))
```


## b 


```{r}
ggplot(df,aes(x)) +
  geom_histogram(aes(y = ..density..), bins = nclass.Sturges(df$x))


```


## c

A continous uniform distribution has the probabilty density function 

\[
f(x) \left\{ \begin{array}{l}
\frac{1}{b-a} \quad a \leq x \leq b \\
0 \quad \quad \text{otherwise}
\end{array}
\right.
\]

Therefore over the interval \([0,1]\) we get:
\[
f(t) = \frac{1}{1-0} = 1
\]

Hence if we integrate to get the cumulative distribution function (for any given \(t\) on the interval)
\[
F(t) = \int 1  =  t \quad \text{for} \quad 0\leq t \leq 1
\]

Now, the main property of the cumulative distribution function is that \(F(x) = Pr(X \leq x)\), thus
\[
F(t)  =  t = Pr(Y \leq t) \quad \text{for} \quad 0\leq t \leq 1
\]
 

## d



## e 

```{r}
n = nrow(df)
df <- df %>% 
  arrange(x) %>% 
  mutate(xi = (row_number()+0.5)/(n+1))

ggplot(df, aes(xi, x))+
  geom_point()

# summary(lm(xi ~ x, data = df))

cor(df$xi, df$x)
```


## f

```{r}
correlation_definer <- function(q){
  df <-  data.frame(w = sort(rnorm(1000))) %>% 
  arrange(w) %>% 
  mutate(x = pnorm(w), xi = (row_number()+0.5)/(q+1))
  cor(df$x, df$xi)
}

cor_list <- sapply(1:100, correlation_definer)
ggplot() +
  geom_histogram(aes(cor_list, y = ..density..), bins = 10)


```
